Technique for \earlywarning\ detection of compact binary coalescence and its implications for multi-messenger astronomy

### 2011-06-12 method.tex
Minor edit in section 2.2.1
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1056 ccdd05d5-56c1-461a-bf98-85f6876523b4

Our goal is to reduce the filtering cost of a
large fraction of the waveform by computing part of the convolution at a lower
sample rate.  Specifically we consider here time slice boundaries with the
smallest power-of-two sample rate that sub-critically samples the time-sliced
template.  The time slices consist of the $S$ intervals
$\left[t^0, t^1\right),\, \left[t^1, t^2\right),\, \dots,\, \left[t^{S-1}, t^S\right)$,
sampled at frequencies $f^0,\, f^1,\, \dots,\, f^\mathrm{S-1}$ where $f^s$ is at
least twice the highest frequency component of any filter in the bank for the $s$th
time slice.

>>>>

Our goal is to reduce the filtering cost of a
large fraction of the waveform by computing part of the convolution at a lower
sample rate.  Specifically we consider here time slice boundaries with the
smallest power-of-two sample rate that sub-critically samples the time-sliced
template.  The time slices consist of the $S$ intervals
$\left[t^0, t^1\right),\, \left[t^1, t^2\right),\, \dots,\, \left[t^{S-1}, t^S\right)$,
sampled at frequencies $f^0,\, f^1,\, \dots,\, f^\mathrm{S-1}$ where $f^s$ is at
least twice the highest nonzero frequency component of any filter in the bank for the
$s$th time slice.
